Download data

### 2024-03-08 scripts/subsetDataforCrews.Rmd
fn for simple phen estimates based on kernel density

blm <- st_read( quiet = T,
  '/media/steppe/hdd/Geospatial_data/Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp') %>% 
  st_transform(5070)

@@

@@

ob <- st_read('/media/steppe/hdd/2024SOS_CrewGeospatial/Eastern Mojave - P102073/Geodata/Species/SDM/Salazaria_mexicana.shp')

```

@@

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
lapply(
  X = teams_list, 
  FUN = phen_tabulator,
  path = p2ts, 
  admu = admin_boundaries, 
  target_species = spp_needed
  )

```

>>>>

blm <- st_read(quiet = T,
  '/media/steppe/hdd/Geospatial_data/Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp') %>% 
  st_transform(5070)

@@

```{r seed zones, eval = F}
seed_zones <- read.csv('../data/raw/2024sos_species-FIXED.csv') %>% 
    unite('binomial', genus:species)

seed_zones %>% 
  filter(stz == 'BowerRevised') %>% 
  distinct(ind_stz) %>% 
  mutate(
    ind_stz = str_replace(ind_stz, '  ', ' ')
  ) %>% 
  separate_wider_delim(ind_stz, delim = ',', names= LETTERS[1:7], too_few = "align_start")

  #  ind_stz = str_replace(ind_stz, ' -[0-9]|[0-9]- |[0-9]-[0-9]', ' - ') )
```

@@

table(STZ$Dataset) 
head(STZ)
```

@@

p2ts <- '/media/steppe/hdd/SeedPhenology/data/processed/timestamps'
ott1 <- lapply(
  X = teams_list[5], # 5 throws an error
  FUN = phen_tabulator,
  path = p2ts, 
  admu = admin_boundaries, 
  target_species = spp_needed
  ) # row 67

ott1[[1]]
```
